Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?

### 2018-04-23 analysis/paper/paper.Rmd
Fix some reference issues and add new

Sheath blight (ShB) disease (*Rhizoctonia solani* Kühn), anastamosis group 1 [(teleomorph: *Thanatephorus cucumeris* (A.B. Frank) Donk.] of rice is an economically important disease worldwide throughout tropical and temperate production areas. The disease can cause up to 44% yield losses [@Marchetti1991] under conducive conditions.

Sheath blight is best managed through an integrated disease management approach which includes resistance [@Kumar2009] fungicide applications where affordable [@Rush1983; @Groth2008], nitrogen management [@Castilla1996; @Slaton2003; @Tang2007] and water management [@Castilla1996].

@@

Because of the interactions between irrigation and N, we established field experiments in order to determine what effects AWD and N had upon ShB incidence and severity.

@@

split-plot N rates differed from the 2015 rates with only two nitrogen treatments, N~3~ (60 kg per ha as urea split into two applications) and N~4~ (180 kg per ha in three splits) was applied.

@@

The authors wish to thank Rachel King University of Southern Queensland Statistical Consulting Unit for her insightful comments on the analysis of this paper, Dale Amozola for technical support in the field. Lastly, Michael Noel, who helped design and manage the first year of the project but passed away in 2015.

>>>>

Sheath blight (ShB) disease (*Rhizoctonia solani* Kühn), anastamosis group 1 [(teleomorph: *Thanatephorus cucumeris* (A.B. Frank) Donk.] of rice is an economically important disease worldwide throughout tropical and temperate production areas. The disease can cause up to 50\% yield losses [@Marchetti1991] under conducive conditions. Studies by Savary et al. [-@Savary2000] estimated yield losses in tropical irrigated lowland rice in Asia at 5-10\%. As resistance is difficult to breed for [@Srinivasachary2011], the disease is best managed through an integrated disease management approach which includes resistance [@Kumar2009] fungicide applications where affordable [@Rush1983; @Groth2008], nitrogen management [@Slaton2003; @Castilla1996; @Tang2007] and water management [@Castilla1996].

@@

Because of the well documented interactions between irrigation and N, we established field experiments to determine what effects AWD and N could have upon ShB incidence and severity in tropical rice.

@@

Split-plot N rates differed from the 2015 rates with only two nitrogen treatments, N~3~ (60 kg per ha as urea split into two applications) and N~4~ (180 kg per ha in three splits) was applied.

@@

The authors wish to thank Rachel King of the University of Southern Queensland Statistical Consulting Unit for her insightful comments on the analysis of this paper. We would also like to thank Dale Amozola, Paul Escandor and P. Lapis for their technical support in the field. Lastly, Michael Noel, who helped design and manage the first year of the project but passed away in September 2016.
